%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref} %Allows for the embedding of urls.
\usepackage{lipsum}

\setlength{\textwidth}{5.1in} % Text width of the document

\newcommand{\comment}[1]{}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jonah Edmundson} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\comment{ \moveleft.5\hoffset\centerline{11612 36A Ave} } % commented out for security reasons
\moveleft.5\hoffset\centerline{Edmonton, AB}
%\moveleft.5\hoffset\centerline{(587) 501-7099}
\comment{\moveleft.5\hoffset\centerline{jonahedmundson (at) gmail (dot) com}}
\moveleft.5\hoffset\centerline{jonahedmundson (at) gmail (dot) com}
%\moveleft.5\hoffset\centerline{\url{www.jonahedmundson.xyz}}
\comment{\moveleft.5\hoffset\centerline{My technical resume is available \href{https://www.jonahedmundson.xyz/edmundson_tech_resume2023.pdf}{here}.}}
%links are provided whenever possible

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{SUMMARY}
%\section{OBJECTIVE}

I have a motley assortment of training and interests, with a bent toward entrepreneurship. I am open to offers. 

%I am a recent data science graduate (4.0 GPA) interested in serving my Edmonton community. My research experience combined with my history in customer service makes me a well-rounded candidate. I am hard-working and eager to learn.
%\lipsum[1][2-5]

%A research position in the field of biology with special interests in medical sciences and data analysis.

%%%%%
%\comment{
%\section{SUMMARY}

%Whether it be weight lifting, trail running, stretching, or martial arts, I have a passion to promote and teach physical health and well-being to others. 
%I am a recent data science graduate (4.0 GPA) interested in computational biology. My research experience combined with my history in customer service makes me a well-rounded candidate. I am hard-working and eager to learn. 
%Ever since taking CTS classes in Jr High, I have had a love for all things culinary. Since this time, I have accumulated experience in several different kitchen settings. 
%}
%%%%%

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Master's of English}, Anticipated 2026 \\
University of Victoria, Victoria, BC 

{\sl Master's of Data Science}, 2023 \\
University of British Columbia Okanagan, Kelowna, BC 

{\sl Bachelor of Science in Biology}, 2022 \\
The King's University, Edmonton, AB \\
Concentration: General Biology \\
Minor: Philosophy

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Owner \& Coach} \hfill Apr 2024 - Oct 2024 \\
\href{https://www.giantsjiujitsu.ca/}{\color{black}{Giants Jiu Jitsu}} 
\begin{itemize} \itemsep -2pt
\item Giants is a jiu jitsu gym that I opened with my brother. We did everything from scratch, including web design, building out the business model, designing the lesson plans, running ads, coaching classes, and everything in between. 
\end{itemize}


{\sl Business Analyst} \hfill Sep 2023 - \textit{Current} \\
Insignia Software Corporation
\begin{itemize} \itemsep -2pt
\item Developing business processes
\item Ensuring software compliance with Alberta government standards 
\item System QA
\end{itemize}


{\sl Shuttle Driver} \hfill Summer 2022 \\
Cathedral Lakes Lodge
\begin{itemize} \itemsep -2pt
\item Driving groups of people up a 1-hour logging road.
\item Vehicle maintenance.
\item Odd jobs to help keep the lodge running.
\end{itemize}

{\sl Undergraduate Researcher} \hfill 2021-22 Academic Term \\
The King's University, Department of Biology
\begin{itemize}
\item Analyzing the flow of substance misuse patients through the emergency department using a multi-state modelling approach. This project was completed for senior credit, and was \href{https://escholarship.org/uc/item/8x79h4xz}{published} in the Western Journal of Emergency Medicine. 
\end{itemize}

{\sl Pizzeria Team Lead} \hfill August 2016 - May 2022 \\
The Stone \& Wheel Pizzeria

\begin{itemize} \itemsep -2pt % Reduce space between items
\item Food and ingredient preparation.
\item Oven management.
\item Cleaning.
\item Communication with customers (working the till, answering phones, etc.)
\end{itemize}

{\sl Undergraduate Researcher} \hfill Summer 2021 \\
University of Alberta, Department of Biology
\begin{itemize}
\item A self directed research-project. The purpose was to investigate whether or not the quality of published studies in 3 major medical education journals changed over the course of the COVID-19 pandemic. Data analysis was completed in R Language.
\end{itemize}

{\sl Teacher's Assistant} \hfill 2020-21 Academic Term \\
The King's University, Department of Chemistry
\begin{itemize}
\item Independently running online labs for alternating groups of students who are not able to be in the physical lab.
\end{itemize}

{\sl Undergraduate Researcher} \hfill Summer 2020 \\
The King's University, Department of Biology
\begin{itemize}
\item From home, reading scientific papers, building biweekly summary reports and presenting findings to a professor (again biweekly).
\par
\small{\textit{Awarded USRA from NSERC for this work.}}
\end{itemize}

{\sl Undergraduate Researcher} \hfill Summer 2019 \\
The King's University, Department of Chemistry
\begin{itemize}
\item In the laboratory helping perform thermodynamic studies on synthetic rubber compounds.
\par
\small{\textit{Awarded USRA from NSERC for this work.}} %%https://cognit.ca/en/research/project/205955
\end{itemize}

{\sl Sprinkler Installation} \hfill Summer 2018 \\
Capital Irrigation
\begin{itemize}
\item Digging holes, installing sprinklers.
\end{itemize}


%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{COMMUNITY \\ SERVICE}


{\it McKernan Baptist Church, 2024/25 Academic Term.} \\
I volunteered as a youth leader with the grade 7 boys.  


{\it Rockridge Canyon, Summer 2023.} \\
I interned at Rockridge Canyon in the Food Service department. This internship was oriented towards leadership skills and Christian discipleship. 


{\it Kelowna Gospel Mission, 2022/23 Academic Term.} \\
I volunteered in the kitchen helping prepare and serve food to those individuals in the reintegration program. 


{\it The King's Running Club, 2019 - 2022.} \\
I started a running club at The King's University with the goal of promoting fitness and community.


{\it The King's Ambassadors, 2018 - 2022.} \\
I volunteered with a group designed to represent the university and help with school-related events (ex. Harvest Banquet, Open House, etc.).

%{\it Edmonton Folk Music Festival, Summer 2019.} \\
%I helped host the festival. I was a part of the security team.

{\it Mexico Missions Trip, Summer 2016.} \\
I helped run a two-week bible camp for underprivileged kids. Role was that of games leader.

%ADD FOLK FEST VOLUNTEERING AND IAC/SA INVOLVEMENT AND KINGS CHRONICLE CONTRIUBUTIONS AND AP NATIONAL SCHOLAR AND NSERCS

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{EXTRA-CURRICULAR \\ ACTIVITIES}

{\it Weekly Running}, Independent. 2018 - Present. \\
{\it Weekly Weight-Lifting}, Independent. 2018 - Present. \\
{\it Brazilian Jiu-Jitsu}, Kingdom MMA, RDC Jiu Jitsu. Summer 2020 - Present.


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS}

{\sl Master of Data Science Domestic Scholarship.}
2022. \\
{\sl Louise McKinney Post-Secondary Scholarship.}
2019, 2020. \\
{\sl Greenfield Community Spirit Memorial Scholarship.} 2019. \\ %%https://www.greenfieldcommunityleague.com/uploads/8/3/2/8/83285180/gazette_mar_apr_19.pdf
{\sl Simona Maaskant Memorial Science Scholarship.} 2019. \\
{\sl Jan and Joan Dejong Scholarship.} 2020. \\
{\sl Academic gold medal (Highest GPA).} 2019, 2020. \\
{\sl Dr. Peter Mahaffy Science Scholarship.} 2021.

\vfill

\section{REFERENCES}

Available upon request.

%----------------------------------------------------------------------------------------

\end{resume}

\end{document}
